Data_visualization

### 2018-10-16 Rmd/Data_visualization_common_names.Rmd
abstract

>>>>

Pollinator sharing can have negative consequences for species fitness with the arrival of foreign pollen. However, the costs of heterospecific pollen are not yet well understood. For this reason, we have conducted a glasshouse experiment where we try to understand how phylogenetic relatedness and the different traits of these species are involved in this process. 10 species belonging to three different families: Brassicaceae, Solanaceae, Convolvulaceae were used and more than 4000 crosses were done and seed set and pollen tubes were considered as proxy of effect. We have found that for all species foreign pollen (50% or less) reduce seed set. Moreover, the seed set reduction is not dependent on the degree of relatedness of the pollen donor. However, the effect is governed on the relatedness and traits of the species recipient. Our results, show that although the effect of heterospecific pollen is species specific, the outcome of it is determine in greater degree by the traits of the pollen recipient than the pollen donor.
